Appendix: Tutorials and examples

### 2017-07-07 appendix.Rmd
Flesh out appendix

---
title: "Appendix: Tutorials and examples"
output:
  github_document:
    toc: yes
  pdf_document: null
---

@@

Many of these resources live primarily on the web and, therefore, are more perishable than the content main text. As time goes on, it is possible that URLs may change, and it might be necessary to use a site's navigation or search features to re-locate the resource.

@@

  * [Git](https://git-scm.com) is a version control system.
  * [RStudio](https://www.rstudio.com/products/rstudio/) is an integrated development environment for R.

@@

@@

  * [Register a free GitHub account](http://happygitwithr.com/github-acct.html)
  * [Install or update R and RStudio](http://happygitwithr.com/install-r-rstudio.html)
  * [Install Git](http://happygitwithr.com/install-git.html) **We have specific reasons for our installation methods, so seriously consider using them!**
  * [Introduce yourself to Git](http://happygitwithr.com/hello-git.html)
  * [Install a Git client](http://happygitwithr.com/git-client.html). Good options -- you might want more than one!
    - [RStudio](https://www.rstudio.com/products/rstudio/) has basic Git client functionality.
    - [SourceTree](https://www.sourcetreeapp.com) is free and excellent.
    - [GitKraken](https://www.gitkraken.com) is also well-regarded and works across Mac OS, Windows, and Linux.
  * [Connect to GitHub](http://happygitwithr.com/push-pull-github.html) will affirm that your system is set up properly.

@@

@@

>>>>

---
title: "Appendix: Tutorials and examples"
output:
  github_document:
    toc: yes
  pdf_document: null
urlcolor: blue    
---

@@

Many of these resources live primarily on the web and, therefore, are more perishable than the content of the article. As time goes on, it is possible that URLs may change, and it might be necessary to use a site's navigation or search features to re-locate the resource.

@@

  * [Git](https://git-scm.com) is a version control system.
  * [RStudio](https://www.rstudio.com/products/rstudio/) is an integrated development environment for R. It can help you use Git and GitHub. More about that below.

@@

I cite it in the article, but really want to underscore the accesibility of Alice Bartlett's talk "Git for Humans". Highly recommended. [Slides on Speakerdeck](https://speakerdeck.com/alicebartlett/git-for-humans).

<https://github.com/jennybc/excuse-me-iris> is the actual Git repository that lead to the screenshots in the figure.

@@

  * [Register a free GitHub account](http://happygitwithr.com/github-acct.html)
  * [Install or update R and RStudio](http://happygitwithr.com/install-r-rstudio.html)
  * [Install Git](http://happygitwithr.com/install-git.html) **We have specific reasons for our installation methods, so seriously consider using them!**
  * [Introduce yourself to Git](http://happygitwithr.com/hello-git.html)
  * [Install a Git client](http://happygitwithr.com/git-client.html). Good options -- you might want more than one!
    - [RStudio](https://www.rstudio.com/products/rstudio/) has basic Git client functionality.
    - [SourceTree](https://www.sourcetreeapp.com) is free and excellent.
    - [GitKraken](https://www.gitkraken.com) is also well-regarded. It is notable in that it runs on Linux, in addition to Mac OS and Windows.
  * [Connect to GitHub](http://happygitwithr.com/push-pull-github.html) will affirm that your system is set up properly.

@@

<https://github.com/jennybc/excuse-me-iris> is the actual Git repository depicted in this figure.

@@

General Git books:

  * [Git in Practice](https://www.manning.com/books/git-in-practice) by Mike McQuaid is my favorite book for day-to-day Git operations.
  * [Pro Git](https://git-scm.com/book/en/v2) by Scott Chacon and Ben Straub is an excellent and comprehensive resource. You can read it for free online.
